Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-30 data_appendix_all_years.Rmd
added probit regression

#model_simple <- lm(assist ~ floods + droughts + year, data = reg_data)
#summary(model_simple)
model_assist <- lm(assist ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
summary(model_assist)
model_register <- lm(register ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
summary(model_register)
model_reason_t <- (lm(work_reason ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data))
summary(model_reason_t)

@@

```{r generate regression table, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist_r, model_register_r), 
               title = "Full sample regression results", 
               label = "fullResults",
               header = F,
               keep = c("floods", "droughts"))
```

@@

rural <- subset(reg_data, rural == 1, select = c("hh_id", "id", "age", "female", "literacy", "dept", "rural", "income", "assist", "register", "floods", "droughts", "year", "child", "grandchild", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor"))

model_assist_r <- (lm(assist ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data))
summary(model_assist_r)
model_register_r <- lm(register ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data)
summary(model_register_r)
model_reason <- (lm(work_reason ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data))
summary(model_reason)

>>>>

#model_simple <- lm(assist ~ floods + droughts + year, data = reg_data)
#summary(model_simple)
#model_assist <- lm(assist ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
#summary(model_assist)
#model_register <- lm(register ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
#summary(model_register)
model_reason_t <- (lm(work_reason ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data))
summary(model_reason_t)

@@

```{r generate regression table, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist_r, model_register_r), 
               title = "Full sample regression results", 
               label = "fullResults",
               header = F,
               keep = c("floods", "droughts"))
```
```{r probit regression total sample}

probitMod_assist <- glm(assist ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data, family=binomial(link="probit"))  # build the logit model

summary(probitMod_assist)  # model summary
```

@@

rural <- subset(reg_data, rural == 1, select = c("hh_id", "id", "age", "female", "literacy", "dept", "rural", "income", "assist", "register", "floods", "droughts", "year", "child", "grandchild", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor", "work_reason"))

model_assist_r <- (lm(assist ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = rural))
summary(model_assist_r)
model_register_r <- lm(register ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = rural)
summary(model_register_r)
model_reason <- (lm(work_reason ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = rural))
summary(model_reason)
